---
title: "Report"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
params:
  a: NA
  b: NA
---

```{r include=FALSE}

library("devtools")
install_github("ipveka/Proc.reg")
library("Proc.reg")

knitr::opts_chunk$set(
	fig.align = "center",
	message = FALSE,
	comment = NA
)

df <- params$a
lm <- params$b

```

<style type="text/css">
p {line-height: 2.5em;}
h1.title {
  font-size: 46px;
  color: Black;
  text-align: center;
}
h1.subtitle {
  font-size: 20px;
  color: Black;
  text-align: center;
}
h4.author {
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
h4.date {
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
</style>

# Data

## Content

```{r}

Proc.reg.content(df)

```

## Summary

```{r}

Proc.reg.summary(df)

```

# Model

## Anova

```{r}

Proc.reg.anova(lm)

```

# Regression

## Estimates

```{r}

Proc.reg.table(lm)

```

## Confidence Intervals

```{r}

Proc.reg.confint(lm)

```

# Testing

## Homocedasticity: White & Breusch-Pagan Test

White test

```{r}

# White test

Proc.reg.white(lm)

```

Breusch-Pagan test

```{r}

# Breusch-Pagan test

Proc.reg.pagan(lm)

```

## Autocorrelation: Durbin Test

```{r}

Proc.reg.durbin(lm)

```

## Linearity: Reset Test

```{r}

Proc.reg.reset(lm)

```

## Multicollinearity: Vif Analysis

```{r}

Proc.reg.vifs(lm)

```
